Extended Abstract

### 2021-05-24 paper/paper.tex
Another pass to the abstract

\begin{abstract}
  To type check a \picalc{} process with linear and shared types without relying on type annotations we need to infer the types of the channels we create within a process.
  If we were to limit ourselves to the shared \picalc{}, we could traverse a process bottom-up and eagerly solve typing constraints into substitutions that are then applied to the typing context.
  However in our setting, typing constraints do not always come with have a most general solution, and thus cannot always be eagerly solved.

  We follow Padovani \cite{Padovani15} and provide a \emph{co-contextual typing inference} \cite{ErdwegBKKM15} algorithm that traverses processes bottom-up and, in addition to the typing context, collects a set of typing constraints.
  We then solve those constraints that have a most general solution by using well-known unification algorithms \cite{McBride03}, and defer the rest until more information becomes available.
  We state clear soundness and completeness theorems for both these phases and a progress theorem that ensures that only those constraints without a most general unifier are deferred.
  The totality of this work is being mechanised in Agda.
\end{abstract}

>>>>

\begin{abstract}
  While a \picalc{} with linear types ensures the privacy and safety of concurrent communication, allowing unrestricted non-linear communication is key to model real-world services.
  To type check a \picalc{} process with linear and shared types without relying on user-provided type annotations we must infer the types of the channels created within the process.
  If we limit ourselves to the shared \picalc{}, we can traverse a process bottom-up and eagerly solve typing constraints into substitutions that are then applied to the typing context.
  However in a setting with both linear and shared types, typing constraints do not always come with have a most general solution, and thus cannot always be eagerly solved.

  We follow Padovani \cite{Padovani15} and provide a \emph{co-contextual typing inference} \cite{ErdwegBKKM15} algorithm that traverses processes bottom-up and, in addition to the typing context, collects a set of typing constraints.
  We then solve those constraints that have a most general solution by using well-known unification algorithms \cite{McBride03}, and defer the rest until more information becomes available.
  We state clear soundness and completeness theorems for both these phases, and a progress theorem that ensures that only those constraints without a most general unifier are deferred.
  The totality of this work is being mechanised in Agda.
\end{abstract}
